paper

### 2022-03-30 outputs/paper.Rmd
bar graph for the comparison of the no child under six and one or more child under six in urban vs rural areas

```{r}

>>>>

```{r, echo = FALSE}
# make dataset in long format
resid_long <- residence %>% 
  select(-c(character)) %>% 
  pivot_longer(!background, names_to = "variables", values_to = "percentage")

# create label names list
label_list <- list('no_child_under_six' = "No child under six", 
                   'one_more_child_under_six' = "One or more child under six")

labellers <- function(variable, value) {
  return(label_list[value])
}

# plot bar graph
resid_long %>% 
  filter(variables == 'no_child_under_six' | variables == 'one_more_child_under_six') %>% 
  ggplot(aes(x = background, 
             y = percentage,
             fill = background)) +
  geom_bar(stat = 'identity',
           fill = "lightblue") +
  labs(x = "Area",
       y = "Percentage of women") +
  theme_minimal() +
  facet_wrap(~variables, labeller = labellers) +
  theme(strip.text = element_text(face = "bold", size = rel(1)),
    strip.background = element_rect(fill = "lightblue", colour = "black", size = 0.5))
```

```{r}
# caretaker aspect
